D3064R0: OOTA Execution on Real Implementations is Provably Vacuous

### 2023-12-28 ootavacuous.tex
Add examples based on Collatz conjecture and on FLT
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

>>>>

But consider the following code fragment:

\begin{quote}
	\co{x = collatz_cycle_min(y);}
\end{quote}

Here, \co{collatz_cycle_min()}\footnote{
	\url{https://en.wikipedia.org/wiki/Collatz_conjecture}}
takes its arbitrary-precision-integer argument and repeatedly either
divides it by two if it is even, or multiplies it by three and adds one
if it is odd.
Should the resulting sequence of arbitrary-precision integers reach
a cycle, the function returns the minimum element of that cycle.
Leaving aside the practical complication of a value of \co{y} that
consumes more than half of the available memory, there is reason to
believe that the above code fragment will always assign the value 1 to
\co{x}.
Except that this reason for belief is based on the Collatz conjecture,
which is unproven and might never be proven.

A similar example could be constructed from Fermat's Last Theorem
(FLT),\footnote{
\url{https://en.wikipedia.org/wiki/Fermat\%27s_Last_Theorem}}
which was first stated in the year 1637 and finally proved more than
300~years later, in 1994.
This of course means that it was only after 1994 that code relying on
FLT was known not to have a semantic dependency.

One could quite reasonably argue that these two examples are irrelevant
to any real-world C++ implementation.
After all, evidence to date suggests that code relying on either the
Collatz Conjecture or FLT is quite rare, and thus not worth optimizing.
And the value of any given optimization is another real-world constraint
on the problem of locating OOTA cycles, but one that will not be considered
further in this document.

\emph{A C++ implementation must assume that a given dependency is
a semantic dependency unless and until it can prove otherwise.}
